Some usefull words/expressions/sentences

### 2018-07-05 phrases.Rmd
LCA analysis by day

>>>>

- Note that because each row of the transition probability matrix is conditioned on Time 1 latent status, this analysis of change in delinquency over time implicitly controls for time 1 delinquency.

- Data can be used from individuals who provide responses to only some questions at a particular time and from those
